---
title: "lab_5"
author: "Hollie Pennington"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    highlight: pygments
    toc: yes
    code_folding: hide
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(effsize)
```

##Part 1: Confidence intervals 

In this section, we'll use the 't.test()' function to calculate confidence intervals. 

### Example 1 

Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample 

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval: 

otter_ci <- t.test(otter_lengths)

# Find the standard deviation 
otter_sd <- sd(otter_lengths)
```

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. 

#### Now, using in-line referencing 

Mean otter length is `r round(otter_ci$estimate, 1)` inches. 



