---
title: "lab_5"
author: "Hollie Pennington"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    highlight: pygments
    toc: yes
    code_folding: hide
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(effsize)
```

##Part 1: Confidence intervals 

In this section, we'll use the 't.test()' function to calculate confidence intervals. 

### Example 1 

Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample 

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval: 

otter_ci <- t.test(otter_lengths)

# Find the standard deviation 
otter_sd <- sd(otter_lengths)
```

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. 

#### Now, using in-line referencing 

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches.  

## Part 2: Two-sample t-tests 

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean? 

```{r}
# make my mock samples 
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

#two-sample t-test 
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# ie.: Trees are drawn from populations with the same mean height
```

If these populations have same mean height there is 28.7% chance that the samples we choose will be at least this different. This is not evidence to reject the null hypothesis. This difference is not very unusual. 

# in a report you would write: 

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r round(trees_t$statistic, 1`), p = `r trees_t$p.value`). 

"t(df) = t-statistic, p = p-value" 

*AVOID*:  p = 0 

When things get really small (usually p < 0.001)

*not great:* p = 0.000000000012 
*better:* p < 0.01 

## Part 3: Another t-test with cars data 

Using the `mpg` dataset 

### Take a look at the data 

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

#check for remaining levels 
unique(compact_suv$class)
```

Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv. 

```{r}
ggplot(data = compact_suv, aes(x = cty)) + 
  geom_histogram(bins = 10) + 
  facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) + 
         geom_qq() + 
         facet_wrap(~ class)
```


Find some summary statistics for each group. 

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = mean(cty), 
    sd_city = sd(cty), 
    sample_size = n()
  )

car_stats
```

The t.test() function REALLY wants vectors of things. Use the 'pull()' funciton to pull out a vector from a data frame. 

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>%  
  pull(cty)

# Your turn: do the same thing to get a vector a city gas mileages for SUVs 

suv_sample <- compact_suv %>% 
  filter (class == "suv") %>%  
  pull(cty)
```


H0: Mean city gas mileages for SUV and compact cars are the same 

```{r}
t.test(compact_sample, suv_sample)
```

There is a significant difference in mean city gas mileage for SUVs and compact cars (t(df)) = t-statistic, p < 0.001). 